The Legacy of the European Post-Master in Urbanism at TU Delft: A Text Mining Approach

### 2023-01-23 analysis/paper/paper.qmd

```{r}
#| label: setup

# Load packages ----
## Package for managing paths
library(here)

## Metapackage for data science
library(tidyverse)

## Packages for text processing and analysis
library(tidytext)
library(SnowballC)
library(tm)

@@

# Read thesis metadata ----
data_path <- here("analysis", "data", "raw_data")
pdf_names <- dir(path, pattern = "*.pdf")

@@

```{r}
#| label: extract-pdf-text
emu_theses$text <- convert_pdf_text(pdf_paths).
```

```{r}
#| label: clean-text

# clean text 
emu_theses$text_clean <- emu_theses$text %>%
  str_replace_all("\\s", " ") %>%  ### remove all carriage return and newline characters
  str_replace_all("- ", "") %>%       ### remove all hyphens
  str_replace_all("[0-9]", "") %>%    ### remove all numbers
  str_replace_all(emu_theses$first_name, "") %>%   ### remove author first name
  str_replace_all(emu_theses$last_name, "") %>%     ### remove author surname
  str_replace_all(emu_theses$title, "") %>%              ### remove title
  str_replace_all("EMU", "") %>%           ### remove common words
  str_squish()
```

@@

The research presented in this paper was prompted by the closure of the European post-Master of Urbanism (EMU) of the Department of Urbanism at the Faculty of Architecture and the Built Environment, TU Delft. 
<!-- Complete paragraph about the program -->

In order to describe the legacy of the EMU program, including the distinctive features of the didactics employed in it, this paper aims to reveal the main topics taught in it and how those topics had evolved through the years of the program. To that end, we employed a text mining approach in which we analysed its output: 97 theses of 100+ pages each produced over the years for the entire duration of the program between 2007-2021.

@@

@@

```{r}
#| label: map-theses
#| warning: false

# Create dummy data
location_names <- as.data.frame(c("Paris, France", "Bucharest, Romania", "Delft, The Netherlands"))

# Geocode

# Visualise thesis locations on world map
world <- map_data("world")
ggplot() +
  geom_map(
    data = world, map = world,
    aes(long, lat, map_id = region),
    color = "black", fill = "lightgray", size = 0.1
  )
```

Word-level tokenisation was applied with the `unnest_tokens()` function of the 
`tidytext` package. This was preferred over other tokenisers as it produced 
results that work seamlessly with other `tidyverse` tools.

Stop words:
- Three types of stop words: global, subject-specific and document stop words.
- Global stop words:
  - All theses were written in English, so for common English stop words the "snowball" lexicon was used
  - Optionally, try creating a custom stop word list on the entire corpus, by removing high-frequency words, starting with 20 words and increasing by 10 until reaching words that are not appropriate as stop words
- Subject-specific stop words:
  - Manually constructed list, needs domain knowledge
  - Words that are commonly used to structure a theses, such as "preface", "contents", and "introduction", were added as custom stop words
- Document stop words:
  - Stop words from titles and author names should only be removed from corresponding theses

@@

<!-- Here's some example analysis code: -->

```{r}
#| label: get-data
#| eval: false
# Note the path that we need to use to access our data files when rendering this document
my_data <- read.csv(here::here('analysis/data/raw_data/my_csv_file.csv'))
```

```{r}
#| label: fig-demo-plot
#| fig-cap: "A plot of random numbers"
plot(rnorm(10))
```

Figure @fig-demo-plot shows how we can have a caption and cross-reference for a plot. Note that figure label and cross-references must both be prefixed with `fig-`

```{r}
#| label: demo-inline-code
#| echo: false
x <- round(pi, 2)
```

Here is an example of inline code `r x` in the middle of a sentence.

>>>>

```{r}
#| label: setup
#| echo: false
#| warning: false

# Load packages ----
## Managing paths
library(here)

## Data manipulation and visualisation
library(tidyverse)

## Text processing and analysis
library(tidytext)
library(SnowballC)
library(tm)

## Working with spatial data
library(tidygeocoder)

@@

# Read thesis metadata ----
## All theses
theses_all <-
  readxl::read_xlsx(path = here("analysis", "data", "raw_data", "theses-all.xlsx"))

## Theses with PDF available
data_path <- here("analysis", "data", "raw_data")
pdf_names <- dir(data_path, pattern = "*.pdf")

@@

```{r}
#| label: extract-pdf-text
#| echo: false
emu_theses$text <- convert_pdf_text(pdf_paths)
```

```{r}
#| label: clean-text
#| echo: false

# clean text 
emu_theses$text_clean <- emu_theses$text %>%
  str_replace_all("\\s", " ") %>%  ### remove all carriage return and newline characters
  # str_replace_all("- ", "") %>%       ### remove all hyphens
  # str_replace_all("[0-9]", "") %>%    ### remove all numbers
  str_replace_all(emu_theses$first_name, "") %>%   ### remove author first name
  str_replace_all(emu_theses$last_name, "") %>%     ### remove author surname
  str_replace_all(emu_theses$title, "") %>%              ### remove title
  str_replace_all("EMU", "") %>%           ### remove common words
  str_squish()
```

```{r}
#| label: preview
#| include: false

# Preview theses
emu_theses %>% 
  arrange(graduation_year) %>% 
  pull(text_clean) %>% 
  str_sub(1, 500)

# Preview theses
hist(str_length(emu_theses$text_clean))

Encoding(emu_theses$text_clean)
```

@@

The research presented in this paper was prompted by the closure of the European post-Master of Urbanism (EMU) of the Department of Urbanism at the Faculty of Architecture and the Built Environment, TU Delft. The EMU was an advanced master ran jointly by TU Delft, KU Leuven, UPC Barcelona and Università IUAV di Venezia. 
<!-- Complete paragraph about the program -->

In order to describe the legacy of the EMU program, including the distinctive features of its didactic approach, this paper aims to reveal the main topics taught in it and how those topics had evolved through the years of the program. To that end, we employed a text mining approach in which we analysed its output: `r nrow(theses_all)` theses with an average of `r mean(str_length(emu_theses$text_clean), na.rm = TRUE)` words produced over the years for the duration of the program between `r paste0(min(theses_all$grad_year, na.rm = TRUE), "-", max(theses_all$grad_year, na.rm = TRUE))`. The first year of the program was not represented, as PDF files were only available from 2008 onward.

@@

A total number of `r nrow(emu_theses)` were analysed.

```{r}
#| label: fig-map-theses
#| warning: false 
#| echo: false
#| fig-cap: "Location of EMU theses included in the analysis"

# Geocode thesis locations
emu_theses <- emu_theses %>%
  geocode(location, method = 'osm', lat = latitude , long = longitude)

# Show thesis locations on world map
world <- map_data("world")
ggplot() +
  geom_map(
    data = world, map = world,
    aes(long, lat, map_id = region),
    color = "black", fill = "lightgray", size = 0.1
  ) +
  geom_point(data = emu_theses, aes(longitude, latitude), color = "red") +
  coord_fixed() +
  theme_void()
```

Figure @fig-map-theses shows the geographic spread of the theses included in the analysis.

@@

### Tokenisation
Word-level tokenisation was applied with the `unnest_tokens()` function of the 
`tidytext` package. This was preferred over other tokenisers as it produced 
results that work seamlessly with other `tidyverse` tools.

### Stop words
- Three types of stop words: global, subject-specific and document stop words.
- Global stop words:
  - All theses were written in English, so for common English stop words the "snowball" lexicon was used
  - Optionally, try creating a custom stop word list on the entire corpus, by removing high-frequency words, starting with 20 words and increasing by 10 until reaching words that are not appropriate as stop words
- Subject-specific stop words:
  - Manually constructed list, needs domain knowledge
  - Words that are commonly used to structure a theses, such as "preface", "contents", and "introduction", were added as custom stop words
- Document stop words:
  - Stop words from titles and author names should only be removed from corresponding theses

@@
